Sky Tomography for 3D Aerosol Distribution Recovery

### 2013-07-26 article.tex
bookmark

Per camera $c$ and voxel $k$, the lines $[{\rm SR},k]$ and $[{\rm
  LOS}_c,k]$ intersect at a fixed angle $\Phi^{\rm scatter}_c(k)$.
Column-stacking all voxels yields the vector representation of all
scattering angles in the domain, $\vect{\Phi}^{\rm scatter}_c$ per
camera $c$. Similarly, the single-scattering albdeos $\varpi^{\rm
  aerosol}$ in all voxels are stacked to vector $\vect{\varpi}$.
Using \cref{eq:alphabasic,eq:rayleighP,eq:betaer,eq:betair}, the
angular scattering coefficients across the domain are expressed in
vector form by
\begin{align}
  \tilde{\vect{\alpha}}^{\rm air}_c &=
  \vect{\beta}^{\rm air} \odot P^{\rm air}(\vect{\Phi}^{\rm scatter}_c) \nonumber \\
  \tilde{\vect{\alpha}}^{\rm aerosol}_c &= \vect{\varpi}\odot
  \vect{\sigma} \odot {\bm n} \odot P^{\rm aerosol}_{\bm
    g}(\vect{\Phi}^{\rm scatter}_c)
  \label{eq:alpha_matrix}
\end{align}
The vector ${\bm g}$ column-stacks the anisotropy parameter of the
phase function, in all voxels. We use this notation, to indicate a
parametric phase function as in \cref{eq:aerosol_scatter}.

>>>>

Per camera $c$ and voxel $k$, the lines $[{\rm SR},k]$ and $[{\rm
  LOS}_c,k]$ intersect at a fixed angle $\Phi^{\rm scatter}_c(k)$.
Column-stacking all voxels yields the vector representation of all
scattering angles in the domain, $\vect{\Phi}^{\rm scatter}_c$ per
camera $c$. Similarly, the single-scattering albdeos $\varpi^{\rm
  aerosol}$ in all voxels are stacked to vector $\vect{\varpi}$.
Using \cref{eq:alphabasic,eq:rayleighP}, the
angular scattering coefficients across the domain are expressed in
vector form by
\begin{equation}
  \tilde{\vect{\alpha}}^{\rm air}_c =
  \vect{\beta}^{\rm air} \odot P^{\rm air}(\vect{\Phi}^{\rm scatter}_c)\;,\quad
  \tilde{\vect{\alpha}}^{\rm aerosol}_c = \vect{\varpi}\odot
  \vect{\sigma} \odot {\bm n} \odot P^{\rm aerosol}_{\bm
    g}(\vect{\Phi}^{\rm scatter}_c)
  \label{eq:alpha_matrix}
\end{equation}
The vector ${\bm g}$ column-stacks the anisotropy parameter of the
phase function, in all voxels. We use this notation, to indicate a
parametric phase function as in \cref{eq:aerosol_scatter}.
